---
title: "Week 4 Part 1 - CI's and t-test"
author: "Grace Kumaishi"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length) #default setting: null hypothesis is a mean value equal to zero, confidence interval and mean are meaningful but p-value is not
```

## T-test (1-sample t-test)

See a claim: mean otter length is 50 inches

```{r}
otter_test <- t.test(x = otter_length, mu = 50)

otter_test
```

## Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns) 
```

Gives mean of x and y (they're pretty close), expected confidence interval for the difference in mean sizes in horn length (less meaningful), p-value tells us that if these samples are drawn from populations with the same mean horn length, there is almost a 90 percent chance that we could have taken two random samples from those two populations and found samples at least as different as the samples that we have here (there is a good chance that we retrieved our samples from populations with the same mean)








